Calculating Entropies With Nested Sampling

### 2017-02-24 paper/ms.tex
Priors for group diff example

\section{Example 2: Measuring the period of an oscillating signal}

>>>>

\section{Example 2: Measuring the difference between two group means}

A basic problem in statistics is the inference of the difference between
two `group mean' parameters $\mu_1$ and $\mu_2$ from data in the form of
samples $\boldsymbol{x} = \{x_1, ..., x_m\}$ and
$\boldsymbol{y} = \{y_1, ..., y_n\}$
The standard frequentist method for this
problem is the two-sample $t$-test, and Bayesian alternatives are
straightforward to specify.

The priors are
\begin{align}
         \mu_1  &\sim \textnormal{Normal}(0,1)     \\
  \ln \sigma_1  &\sim \textnormal{Normal}(0,1)     \\
         d_\mu  &\sim \textnormal{Normal}(0,1)     \\
 d_{\ln \sigma} &\sim \textnormal{Normal}(0,0.1^2) \\
         \mu_2  &\leftarrow \mu_1 + d_\mu          \\
  \ln \sigma_2  &\leftarrow \ln \sigma_1 + d_{\ln \sigma}
\end{align}
and the conditional prior for the data given the parameters is
\begin{align}
x_i &\sim \textnormal{Normal}\left(\mu_1, \sigma_1^2\right) \\
y_i &\sim \textnormal{Normal}\left(\mu_2, \sigma_2^2\right)
\end{align}

\section{Example 3: Measuring the period of an oscillating signal}
